Automated topic naming to support analysis of software maintenance activities

### 2010-08-18 icse/icse2011.tex
CLR and Mulan segway

The less-frequently occurring a label the harder it is to get accurate results, due to the high noise level. Nevertheless, these results are better than our previous word bag results of \textsf{exp2} and \textsf{exp3}, because the ROC values are sufficiently higher in most cases (other than MaxDB reliability and MySQL efficiency). The limitation of the approach we took here is that we assume labels are independent; however, labels could be correlated with each other. We also did not evaluate how well the learners performed together.
\todo[inline]{Comment about correlation, we should link to the Mulan section, perfect segway since Mulan relies on correlation.}

@@

\subsection{Applying multiple labels to topics}
As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero to all NFRs. For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement in the source code that related to \textit{usability}. However, traditional machine learning techniques, such as Bayesian networks, can only map topics to a single class. The Mulan~\cite{mulan} library encapsulates several different machine learners which can handle this multi-label learning for our data-set. Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

Fig. \ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. %Calibrated Label Ranking (CLR)
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. These classifiers performed better than other multi-label classifiers. They have the best micro and macro ROC scores, although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplearn}.
\todo[inline]{discuss this similarity in more detail}
\todo[inline]{what of CLR? Is it hierarchical?}

>>>>

The less-frequently occurring a label the harder it is to get accurate
results, due to the high noise level. Nevertheless, these results are
better than our previous word bag results of \textsf{exp2} and
\textsf{exp3}, because the ROC values are sufficiently higher in most
cases (other than MaxDB reliability and MySQL efficiency). The
limitation of the approach we took here is that we assume labels are
independent; however, labels could be correlated with each other. 
The next section, Section \ref{sec:multilabel} on multi-labels
addresses the issue of a lack of independence and correlation between labels.
In the next section we will evaluate how well these learners perform
together.
%\todo[inline]{Comment about correlation, we should link to the Mulan section, perfect segway since Mulan relies on correlation.}

@@

\subsection{Applying multiple labels to topics}
\label{sec:multilabel}

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero to all NFRs. For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement in the source code that related to \textit{usability}. However, traditional machine learning techniques, such as Bayesian networks, can only map topics to a single class. The Mulan~\cite{mulan} library encapsulates several different machine learners which can handle this multi-label learning for our data-set. Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

Fig. \ref{fig:mulan} presents the results of Mulan's best multi-label
learners for our data. Calibrated Label Ranking (CLR) is a learner
that builds two layers, the first layer determines if an entity should
be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. These classifiers performed better than other multi-label classifiers. They have the best micro and macro ROC scores, although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplearn}.
\todo[inline]{discuss this similarity in more detail}
%\todo[inline]{what of CLR? Is it hierarchical?}
